---
title: "House Prices"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mice)
library(randomForest)
library(modelr)
test<-read_csv("test.csv")
train<-read_csv("train.csv")

```

Combine the train and test set so I can make modifications to the variables and such to both the train and test set.
```{r include=TRUE}
total<-bind_rows(train,test)
```

```{r echo=TRUE}
head(train)
```
#Data exploration

```{r echo=TRUE}
total %>% 
  ggplot() +
  geom_point(aes(x=LotArea,y=SalePrice))
```

# Cleaning the data

Let's figure out which columns have NA's and how bad our situation is. 

```{r echo=TRUE}
apply(apply(total,2,is.na),2,sum)
```

We can ignore the number of NAs for SalePrice since those just correspond to the test set. We can see that there are many NA's for LotFrontage. 

The NA's for Alley is actually information. NA means no alley access, so we change the NA's of Alley to that.

```{r echo=TRUE}
total$Alley[is.na(total$Alley)]="No alley access"

```

Do the same for the other variables that list NA as a value

```{r echo=TRUE}

bsmt_nas<-which((is.na(total$BsmtCond) &
        is.na(total$BsmtExposure) &
        is.na(total$BsmtFinType1) &
        is.na(total$BsmtFinType2) &
        is.na(total$BsmtQual) &
        is.na(total$TotalBsmtSF)) | total$TotalBsmtSF==0)

bsmt<-total[bsmt_nas,]
```

There is a row in bsmt that has NAs in the basement square footage variables as well. We will set the rest of these to 0.

```{r echo=TRUE}
bsmt[53,] %>%
  select(BsmtQual:TotalBsmtSF)
```

```{r echo=TRUE}
total$BsmtCond[bsmt_nas]<-"No basement"
total$BsmtExposure[bsmt_nas]<-"No basement"
total$BsmtFinType1[bsmt_nas]<-"No basement"
total$BsmtFinType2[bsmt_nas]<-"No basement"
total$BsmtQual[bsmt_nas]<-"No basement"
total$BsmtFinSF1[bsmt_nas]<-0
total$BsmtFinSF2[bsmt_nas]<-0
total$BsmtUnfSF[bsmt_nas]<-0
total$BsmtHalfBath<-0
total$BsmtFullBath<-0
total$TotalBsmtSF[bsmt_nas]<-0
```

We still have some basement fields with NAs here, but I can't see any pattern among them.

Fireplaces has no NAs, but Fireplace quality has a bunch.

```{r echo=TRUE}
total$FireplaceQu[total$Fireplaces==0 & is.na(total$FireplaceQu)]<-"No fireplace"
which(is.na(total$FireplaceQu))
```

Fix pool problems, but we are still left with NA's in the test set 
```{r echo=TRUE}
total$PoolQC[total$PoolArea==0&is.na(total$PoolQC)]<-"No pool"
which(is.na(total$PoolQC))
```

```{r echo=TRUE}
garage_nas<-total$GarageArea==0 | (
  is.na(total$GarageArea) & 
  is.na(total$GarageCars) &      
  is.na(total$GarageCond) &
  is.na(total$GarageFinish) & 
  is.na(total$GarageQual) & 
  is.na(total$GarageType) &
  is.na(total$GarageYrBlt))
total$GarageArea[garage_nas]<-0
total$GarageCars[garage_nas]<-0
total$GarageCond[garage_nas]<-"No garage"
total$GarageFinish[garage_nas]<-"No garage"
total$GarageQual[garage_nas]<-"No garage"
total$GarageType[garage_nas]<-"No garage"
total$GarageYrBlt[garage_nas]<-NA #Not sure what to do here yet
```


```{r echo=TRUE}
total$Fence[is.na(total$Fence)]="No fence"
```


For MiscFeature, we will also treat NAs as just no extra feature

```{r echo=TRUE}
total$MiscFeature[is.na(total$MiscFeature)]<-"None"
```


How many NAs have we removed?

```{r echo=TRUE}
apply(apply(total,2,is.na),2,sum)
```

Treat each case individually, just replace with modes and medians

```{r echo=TRUE}
total$MSZoning[is.na(total$MSZoning)]=mode(total$MSZoning)
total$Utilities[is.na(total$Utilities)]=mode(total$Utilities)
total$Exterior1st[is.na(total$Exterior1st)]=mode(total$Exterior1st)
total$Exterior2nd[is.na(total$Exterior2nd)]=mode(total$Exterior2nd)
total$MasVnrType[is.na(total$MasVnrType)]=mode(total$MasVnrType)
total$MasVnrArea[is.na(total$MasVnrArea)]=median(total$MasVnrArea,na.rm=TRUE)
total$BsmtQual[is.na(total$BsmtQual)]=mode(total$BsmtQual)
total$BsmtCond[is.na(total$BsmtCond)]=mode(total$BsmtCond)
total$BsmtExposure[is.na(total$BsmtExposure)]=mode(total$BsmtExposure)
total$BsmtFinType2[is.na(total$BsmtFinType2)]=mode(total$BsmtFinType2)
total$Electrical[is.na(total$Electrical)]=mode(total$Electrical)
total$KitchenQual[is.na(total$KitchenQual)]=mode(total$KitchenQual)
total$Functional[is.na(total$Functional)]=mode(total$Functional)
total$GarageFinish[is.na(total$GarageFinish)]=mode(total$GarageFinish)
total$GarageCars[is.na(total$GarageCars)]=median(total$GarageCars,na.rm=TRUE)
total$GarageArea[is.na(total$GarageArea)]=median(total$GarageArea,na.rm=TRUE)
total$GarageQual[is.na(total$GarageQual)]=mode(total$GarageQual)
total$GarageCond[is.na(total$GarageCond)]=mode(total$GarageCond)
total$PoolQC[is.na(total$PoolQC)]=mode(total$PoolQC)
total$SaleType[is.na(total$SaleType)]=mode(total$SaleType)

```

```{r echo=TRUE}
apply(apply(total,2,is.na),2,sum)
```
Use the mice package to impute the LotFrontage

```{r echo=FALSE}
set.seed(927)

total<-type_convert(total,cols(MSSubClass=col_character(),MoSold=col_character()))

#gather all the names of the columns that are factors
fact_vars <- total %>%
  summarise_all(class) %>%
  gather() %>%
  filter(value=="character") %>%
  .[["key"]]

total <- total %>%
  mutate_if(is.character,as.factor)

#select the variables we want for the mice model
mice_subset <- total %>%
  select(-Id,-Condition1,-Condition2,-(BsmtQual:Electrical),-(BsmtFullBath:BsmtHalfBath),-SalePrice,-GarageYrBlt)
  
mice_mod<-mice(mice_subset,method='rf')
mice_output<-complete(mice_mod)

total$LotFrontage<-mice_output$LotFrontage
```
```{r echo=TRUE}
apply(apply(total,2,is.na),2,sum)
```
```{r echo=TRUE}

#take log of saleprice

total <- total %>% mutate(SalePrice=log(SalePrice))

#change variable names that give randomforest problems
names(total)[names(total)=="1stFlrSF"]<-"FirstFlrSF"
names(total)[names(total)=="2ndFlrSF"]<-"SecondFlrSF"
names(total)[names(total)=="3SsnPorch"]<-"ThirdSsnPorch"

#separate the training and test data again for the prediction
train <- total %>%
  filter(!is.na(SalePrice)) %>%
  select(-MSZoning,-GarageYrBlt,-Id,-LotFrontage)
test <- total %>%
  filter(is.na(SalePrice)) %>%
  select(-MSZoning,-GarageYrBlt,-Id,-LotFrontage)

model<-randomForest(SalePrice ~ ., data=train)

prediction<-predict(model, test)

output <- test %>%
  add_predictions(model,"lSalePrice") %>%
  mutate(SalePrice=exp(lSalePrice)) %>%
  select(SalePrice)


preds<-total %>% filter(is.na(SalePrice)) %>%select(Id) %>% cbind(output)
write_csv(preds,"sub.csv")
```

Try XGBoost 
```{r echo=TRUE}
total_num<-total %>%
  mutate_if(is.factor,as.integer)

train <- total_num %>%
  filter(!is.na(SalePrice)) %>%
  select(-GarageYrBlt,-Id)

test <- total_num %>%
  filter(is.na(SalePrice)) %>%
  select(-GarageYrBlt)

trainD<- xgb.DMatrix(data=as.matrix(train[,names(train)!="SalePrice"]),label=as.matrix(train[,"SalePrice"]))

cv.sparse <- xgb.cv(data = trainD,
                    nrounds = 500,
                    min_child_weight = 0,
                    max_depth = 10,
                    eta = 0.02,
                    subsample = .7,
                    colsample_bytree = .7,
                    booster = "gbtree",
                    eval_metric = "rmse",
                    verbose = TRUE,
                    print_every_n = 50,
                    nfold = 4,
                    nthread = 2,
                    objective="reg:linear")

xgb.mod<-xgb.train(params=cv.sparse$params,data=trainD, nrounds=1000,print_every_n=100)


prediction <- predict(xgb.mod, as.matrix(test))

submission<-cbind(Id=as.character(test$Id),SalePrice=exp(prediction))

```
